### 2024-07-14 base-rates.qmd
20240714 - cross-ref

Conversely (and rearranging the terms for the calculation of [conditional probability](#sec-conditionalProbability)), a [joint probability](#sec-jointProbability) can also be calculated using the [conditional probability](#sec-conditionalProbability) and [marginal probability](#sec-baseRate), as in @jointProbability2:

@@

The negative likelihood ratio (LR−) compares the false negative rate to the true negative rate.
Negative likelihood ratio values range from 0 to 1.
Smaller values reflect greater accuracy, because it indicates that a false negative is less likely than a true negative.
The formula for calculating the negative likelihood ratio is in @negativeLikelihoodRatio.

$$
\begin{aligned}
  \text{negative likelihood ratio } (\text{LR}-) &= \frac{\text{FNR}}{\text{TNR}} \\
  &= \frac{P(\text{not } R|C)}{P(\text{not } R|\text{not } C)} \\
  &= \frac{1 - P(R|C)}{P(\text{not } R|\text{not } C)} \\
  &= \frac{1 - \text{sensitivity}}{\text{specificity}}
\end{aligned}
$$ {#eq-positiveLikelihoodRatio}

>>>>

Conversely (and rearranging the terms for the calculation of [conditional probability](#sec-conditionalProbability)), a [joint probability](#sec-jointProbability) can also be calculated using the [conditional probability](#sec-conditionalProbability) and [marginal probability](#sec-baseRate), as in @eq-jointProbability2:

@@

The negative likelihood ratio (LR−) compares the false negative rate to the true negative rate.
Negative likelihood ratio values range from 0 to 1.
Smaller values reflect greater accuracy, because it indicates that a false negative is less likely than a true negative.
The formula for calculating the negative likelihood ratio is in @eq-negativeLikelihoodRatio.

$$
\begin{aligned}
  \text{negative likelihood ratio } (\text{LR}-) &= \frac{\text{FNR}}{\text{TNR}} \\
  &= \frac{P(\text{not } R|C)}{P(\text{not } R|\text{not } C)} \\
  &= \frac{1 - P(R|C)}{P(\text{not } R|\text{not } C)} \\
  &= \frac{1 - \text{sensitivity}}{\text{specificity}}
\end{aligned}
$$ {#eq-negativeLikelihoodRatio}
